Evolution of precopulatory and postcopulatory inbreeding behaviour

### 2016-08-31 ms_pre_post.Rmd
Revise end paragraph of introduction

Here we apply a model of female and male reproductive interactions and associated inbreeding depression in offspring viability to quantify evolution of three separate traits including female tendency for polyandry, female pre-copulatory inbreeding strategy (mating strategy), and female post-copulatory inbreeding strategy (fertilisation strategy). We use *in silico* experiments to test the hypotheses that evolution of post-copulatory inbreeding avoidance facilitates evolution of polyandry, and that evolution of pre-copulatory versus post-copulatory inbreeding avoidance can be predicted by the relative costs of each, and the relative cost of polyandry. We thereby provide a framework for predicting evolution of pre-copulatory and post-copulatory inbreeding avoidance across reproductive systems with different relative costs and different magnitudes of inbreeding depression in offspring viability.

>>>>

Here we apply a model of female and male reproductive interactions and associated inbreeding depression in offspring viability to quantify evolution of three separate traits including female tendency for polyandry, female pre-copulatory inbreeding strategy (mating strategy), and female post-copulatory inbreeding strategy (fertilisation strategy). We use *in silico* experiments to test the hypotheses that, given inbreeding depression in offspring viability, evolution of post-copulatory inbreeding avoidance facilitates evolution of polyandry, and that pre-copulatory but not post-copulatory inbreeding avoidance will evolve when pre-copulatory inbreeding avoidance is less costly than the combined cost of post-copulatory inbreeding avoidance and polyandry, while post-copulatory but not pre-copulatory inbreeding avoidance will evolve when pre-copulatory inbreeding avoidance is more costly than the combined costs of post-copulatory inbreeding avoidance and polyandry. We thereby provide a framework for predicting evolution of pre-copulatory and post-copulatory inbreeding avoidance across reproductive systems with different relative costs and different magnitudes of inbreeding depression in offspring viability.
